\textbf{Department Invited Speakers Do Not Reflect Trainee Diversity}

### 2019-09-20 submission/manuscript.Rmd
add references and text from JL & RP

---
title: '**Department Invited Speakers Do Not Reflect Trainee Diversity**'
csl: mbio.csl
fontsize: 10pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
geometry: margin=1.0in
---

@@

500 words

Representation of white women and historically underrepresented minorities (HURM) in science, technology, engineering, and math (STEM) in the workforce remains low despite equal enrollment in undergraduate STEM majors. Longitudinal data indicates that these discrepancies might be partially explained by low retention of women and URM in undergraduate STEM programs where academic performance is a key predictor of retention. A growing body of evidence suggests that women and URM under-perform in introductory science courses compared to their white male colleagues, even when representation is equal. Additionally, there is evidence to suggest that women and URM participate less in class, which could inhibit the learning process and subsequent success. A prevailing hypothesis to explain achievement gaps and a lack of participation in class for women and URM is that, many students have an unconscious fear of being seen as a negative stereotype, termed stereotype threat. This is prevalent in fields that have historically been dominated by white males, such as in STEM. In order to retain a diverse population of students in STEM, in an effort to ensure all students have equal opportunities and resources to be successful, under-performance and a lack of participation in introductory science courses needs to be addressed. One mechanism to address the issue is through the use of inclusive teaching practices –teaching methods that promote the full participation, learning, and success of all students.

+ introduce invited speaker series - what are the goals, who attends, etc.

+ previous examinations have focused on conferences and panels, large number of people in a short period of time -- easy to make comparisons & see trends

+ more difficult to see trends over long time period -- asked cumulative trends of speakers over 5 year period, "normative" to trainees in the department

@@

@@

cauc_lect <- lect_summary %>% 
  filter(demographic == "Caucasian") %>% 
  summarise(sum = sum(n))
```
To understand the representation of women, we compared the proportion of women in each academic role. At the trainee level, more than half of students and postdoctoral fellows were women. That dropped to `r gender_combined[[1,4]]`% of faculty hosts and `r gender_combined[[3,4]]`% of the invited speakers (Fig. 1A). Of `r sum(lect_summary$n)` lectureships over the five year period, `r lect_summary[4,4]`% were awarded to women. The proportion of women as faculty hosts and speakers is equivalent to global estimates that 40% of microbiologists are women (Elseiver), with a slightly lower representation of women in lectureships.

@@

@@

Several papers have investigated the representation of women at scientific conferences, however, we have only identified one that focused on invited speakers at universities (Nittrouer, 2018). In their study, Nittrouer et. al., examined 3,652 talks at 50 U.S. institutions in 2013 - 2014 and found that women faculty are less likely to be invited speakers, despite similar acceptance rates. These results suggest that women faculty are less often invited as speakers, a decision that may be negatively impacted by assumptions about competency and dedication. The dedication of women who have children to their work is perceived to be less than that of their colleagues, i.e., men who also have children. The perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation (despite the prestigious nature of these invitations and evidence to the contrary). As a result, the faculty member invites a different colleague who they feel is more likely to agree (and is a man). Departments have different processes and criteria for selecting invited speakers, but it is a matter of pride to bring the best scientists possible. It may be that the definition of "best" poses a problem to women, who need three-times as many publications as their men colleges to be considered equally competent. Some departments only invite tenured faculty, which severely limits the number of potential women speakers. Another scenario is that pre-tenure faculty members invite prestigious, tenured faculty in their field to network and secure letters for their own tenure package. The increased burden of women to prove competency decreases their likelihood to be considered for either tenure or as possible source of tenure letters.

@@

@@

+ Development of Diversify tools
    + describe maintenance of lists (Rebecca)

The website provides an interface to the Google forms and spreadsheets with template pages for viewing the list, adding a name to the list, and finding additional resources. Importantly, our website creation tool is hosted for free by GitHub, which provides a free website for each GitHub organization (citation). Basic tools and skills required to set up a Diversify site include knowledge of, or experience with, the version control tool git, the webtool GitHub, and a text editor. A tutorial in the DiversifyMicrobiology repository on GitHub provides links to these resources and instructions for adapting the tool to your own field.

@@

## Author Contributions
A.K.H. collected the data, assigned demographics, analyzed the data, and created the website. R.M.P. created the Google lists, forms, and website content and the description of their maintenance. J.L. wrote the introduction and provided conceptual advice. All authors contributed to the final manuscript.

>>>>

---
title: '**Department Invited Speakers Do Not Reflect Trainee Diversity**'
csl: mbio.csl
fontsize: 10pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
geometry: margin=1.0in
bibliography: references.bib
---

@@

Long-standing systemic bias, sexism, and racism have contributed to the underrepresentation of many racial and ethnic groups, as well as women, in science, technology, engineering, and math (STEM) fields (NIH 2015 report, Measuring DEI 2016, [@colloquy_2012]). Organization climate and culture that supports inclusion of all individuals is essential to support the retention of historically underrepresented minorities (HURM) in the U.S., as well as non-Caucasian individuals, and women in STEM fields (Schneider, 2013). Inclusive organization culture will not suffice in retaining HURM, non-Caucasian individuals, and women without organization policy changes that support their values and goals [@Coe2019].

A long-standing issue within STEM fields, specifically within academia, has been a lack of diverse representation of scientists for trainees (graduate students and postdoctoral fellows). In order to maintain retention of HURM, non-Caucasian individuals, and women in STEM fields, it is important for trainees to have visual representations of themselves as scientists. The importance of representation in retaining a diverse group of individuals in STEM fields is supported by social role theory [@Eagly1984]. Individuals tend to make inferences about characteristics that are needed to be successful in a given role by examining individuals that most occupy that role [@Eagly1984; @Carter2018]. Therefore, trainees who do not see representation of themselves in senior scientific positions, or in this case as senior faculty members, may decide that they do not possess the characteristics that are required to succeed. In an attempt to make science a more inclusive environment, many individuals have attempted to address this issue by promoting the inclusion of more women speakers at conferences [@kalejta_gender_2017; @casadevall_presence_2014; @klein_speaking_2017]. However, no study to date has addressed invited speaker seminar series diversity within their own institution.

Within the Department of Microbiology and Immunology at the University of Michigan (Ann Arbor, MI, USA), each year from September to June, faculty members have the opportunity to invite scientists from other institutions to give a one-hour seminar in which all department members attend. The invited seminar speaker also has the opportunity to meet with current department faculty members and trainees. Scientists who are invited to give seminars are widely regarded as successful and the top in their field. Thus, if trainees are constantly being exposed to “the top scientist in their field”, according to social role theory, it is imperative that the selected seminar speakers represent a diverse group of individuals.

In this study, we examine and compare the proportion of HURM, non-Caucasian/non-HURM, and women invited speakers to white males in the Department of Microbiology and Immunology. Additionally, we compare invited-speaker demographics to the current trainee demographics as a means to gauge if trainee demographics are being represented accordingly throughout the seminar series. Following our investigation, we proposed a policy change to the Department of Microbiology and Immunology in how invited speakers are selected as a means to promote inclusion in our department and reduce stereotype threat, microaggressions, and unconscious bias. In order to facilitate inviting a more diverse group of scientists, we developed a set of resources that allow scientists, within the field of microbiology, to self-identify as an HURM, non-Caucasian/non-HURM, or a woman. These resources will promote inclusion and diversity by providing greater representation of all scientists and will provide hosts an opportunity to invite a more diverse group of scientists.

@@

Data were analyzed and figures generated in R Statisical Software, using the tidyverse package [@wickham_tidyverse:_2017].

@@

cauc_lect <- lect_summary %>% 
  filter(demographic == "Caucasian") %>% 
  summarise(sum = sum(n))
```
To understand the representation of women, we compared the proportion of women in each academic role. At the trainee level, more than half of students and postdoctoral fellows were women. That dropped to `r gender_combined[[1,4]]`% of faculty hosts and `r gender_combined[[3,4]]`% of the invited speakers (Fig. 1A). Of `r sum(lect_summary$n)` lectureships over the five year period, `r lect_summary[4,4]`% were awarded to women. The proportion of women as faculty hosts and speakers is equivalent to global estimates that 40% of microbiologists are women, with a slightly lower representation of women in lectureships [@allagnat_gender_2017].

@@

+ HURM represent 10% of assistant prof, falls to 5% of full [@whittaker_retention_2015]

+ 2017 doctorates in Micro/immuno = 26,250 -- [@nsf_survey_2017]
HURM = `r get_percent((1350+450+1000),26250)` -- 11%
NCNH = `r get_percent((5350+450),26250)` -- 22%

@@

Several papers have investigated the representation of women at scientific conferences, however, we have only identified one that focused on invited speakers at universities [@nittrouer_gender_2018]. In their study, @nittrouer, examined 3,652 talks at 50 U.S. institutions in 2013 - 2014 and found that women faculty are less likely to be invited speakers, despite similar acceptance rates. These results suggest that women faculty are less often invited as speakers, a decision that may be negatively impacted by assumptions about competency and dedication. The dedication of women who have children to their work is perceived to be less than that of their colleagues, i.e., men who also have children. The perceived prioritization and commitments of women to family over work may cause faculty to doubt their acceptance of a speaking invitation (despite the prestigious nature of these invitations and evidence to the contrary)[@nittrouer_gender_2018; @xu_2008]. As a result, the faculty member invites a different colleague who they feel is more likely to agree (and is a man). Departments have different processes and criteria for selecting invited speakers, but it is a matter of pride to bring the best scientists possible. It may be that the definition of "best" poses a problem to women, who need three-times as many publications as their men colleges to be considered equally competent. Some departments only invite tenured faculty, which severely limits the number of potential women speakers. Another scenario is that pre-tenure faculty members invite prestigious, tenured faculty in their field to network and secure letters for their own tenure package. The increased burden of women to prove competency decreases their likelihood to be considered for either tenure or as possible source of tenure letters.

The desire to invite the “best” scientist to these seminar series also poses a problem for HURM and NCNH scientists. Both men and women who identify as HURM and Asian reported having to work harder than their white male colleagues to be perceived as legitimate scholars [@noauthor_seeking_2013]. The proportion of HURM faculty at the Assistant and Associate Professor level is currently higher than the Full Professor level so it will be difficult to increase speaker diversity if early-career researchers are not being considered [@whittaker_retention_2015]. These differences in performance expectations and patterns of exclusions are consistent themes in studies characterizing the HURM faculty experience [@pololi_race_2010; @hassouneh_experiences_2014]. These experiences decrease the opportunities for HURM and NCNH scientists to network, secure letters for their own tenure package, and promote their work for consideration of award nominations.

@@

# Instituting policy change within the Department of Microbiology and Immunology

In an attempt to promote inclusion within the Dept. M&I these data were presented to faculty members and the dept chair (Harry Mobley). Since, trainee demographics were not represented within seminar speaker demographics over the past 5 years, we proposed a policy change as to how seminar speakers were being invited. This policy change included switching from PI invited to lab invited in an attempt to allow trainees to choose a speaker that best represented themselves. In addition to this we also created resources which allowed scientists to self-identify and provide host faculty with more diverse choices.

@@

The self-nomination form is a Google Form with entries logged in a private Google Sheet. This form is embedded within the website and can be linked to directly. The use of a Google Forms allows us to maintain this database at no cost and gives us the flexibility to add questions or change response options without disrupting previous responses. Entries are logged in a private spreadsheet so that entries can be screened before being added to the public database. This screening currently includes two steps: 1. Confirming that each person is listed in the database only once. 2. Verifying that the submitted website is a professional website for the person being listed. If a person has not been listed in the database previously and passes step 2, a new entry is added to the public database spreadsheet. If a person is already listed in the database, their information is updated to the most recent submission.

This public spreadsheet is embedded in the website and can be open separately as a locked (uneditable) Google Sheet. Importantly, this allows the list to be easily searched. We have chosen to list individuals’ academic information first in the spreadsheet to encourage a focus on academic achievement rather than tokenization of marginalized identities. Currently the database lists individuals in order of self-nomination but future versions will be re-sorted based on name and/or academic field to varying the individuals who may receive more attention for simply being at the top of the list.

The website provides an interface to the Google forms and spreadsheets with template pages for viewing the list, adding a name to the list, and finding additional resources. Importantly, our website creation tool is hosted for free by GitHub, which provides a free website for each GitHub organization. Basic tools and skills required to set up a Diversify site include knowledge of, or experience with, the version control tool git, the webtool GitHub, and a text editor. A tutorial in the DiversifyMicrobiology repository on GitHub provides links to these resources and instructions for adapting the tool to your own field.

@@

## Author Contributions
A.K.H. collected the data, assigned demographics, analyzed the data, and created the website. R.M.P. created the Google lists, forms, and website content and the description of their maintenance. J.L. wrote the introduction and provided conceptual advice. All authors contributed to preparing the final manuscript.

### 2019-09-20 submission/manuscript.tex
add references and text from JL & RP

500 words

Representation of white women and historically underrepresented
minorities (HURM) in science, technology, engineering, and math (STEM)
in the workforce remains low despite equal enrollment in undergraduate
STEM majors. Longitudinal data indicates that these discrepancies might
be partially explained by low retention of women and URM in
undergraduate STEM programs where academic performance is a key
predictor of retention. A growing body of evidence suggests that women
and URM under-perform in introductory science courses compared to their
white male colleagues, even when representation is equal. Additionally,
there is evidence to suggest that women and URM participate less in
class, which could inhibit the learning process and subsequent success.
A prevailing hypothesis to explain achievement gaps and a lack of
participation in class for women and URM is that, many students have an
unconscious fear of being seen as a negative stereotype, termed
stereotype threat. This is prevalent in fields that have historically
been dominated by white males, such as in STEM. In order to retain a
diverse population of students in STEM, in an effort to ensure all
students have equal opportunities and resources to be successful,
under-performance and a lack of participation in introductory science
courses needs to be addressed. One mechanism to address the issue is
through the use of inclusive teaching practices --teaching methods that
promote the full participation, learning, and success of all students.

\begin{itemize}
\item
  introduce invited speaker series - what are the goals, who attends,
  etc.
\item
  previous examinations have focused on conferences and panels, large
  number of people in a short period of time -- easy to make comparisons
  \& see trends
\item
  more difficult to see trends over long time period -- asked cumulative
  trends of speakers over 5 year period, ``normative'' to trainees in
  the department
\end{itemize}

@@

@@

To understand the representation of women, we compared the proportion of
women in each academic role. At the trainee level, more than half of
students and postdoctoral fellows were women. That dropped to 46.77\% of
faculty hosts and 38.73\% of the invited speakers (Fig. 1A). Of 27
lectureships over the five year period, 37.04\% were awarded to women.
The proportion of women as faculty hosts and speakers is equivalent to
global estimates that 40\% of microbiologists are women (Elseiver), with
a slightly lower representation of women in lectureships.

@@

@@

Several papers have investigated the representation of women at
scientific conferences, however, we have only identified one that
focused on invited speakers at universities (Nittrouer, 2018). In their
study, Nittrouer et. al., examined 3,652 talks at 50 U.S. institutions
in 2013 - 2014 and found that women faculty are less likely to be
invited speakers, despite similar acceptance rates. These results
suggest that women faculty are less often invited as speakers, a
decision that may be negatively impacted by assumptions about competency
and dedication. The dedication of women who have children to their work
is perceived to be less than that of their colleagues, i.e., men who
also have children. The perceived prioritization and commitments of
women to family over work may cause faculty to doubt their acceptance of
a speaking invitation (despite the prestigious nature of these
invitations and evidence to the contrary). As a result, the faculty
member invites a different colleague who they feel is more likely to
agree (and is a man). Departments have different processes and criteria
for selecting invited speakers, but it is a matter of pride to bring the
best scientists possible. It may be that the definition of ``best''
poses a problem to women, who need three-times as many publications as
their men colleges to be considered equally competent. Some departments
only invite tenured faculty, which severely limits the number of
potential women speakers. Another scenario is that pre-tenure faculty
members invite prestigious, tenured faculty in their field to network
and secure letters for their own tenure package. The increased burden of
women to prove competency decreases their likelihood to be considered
for either tenure or as possible source of tenure letters.

@@

@@

\begin{itemize}
\tightlist
\item
  Development of Diversify tools

  \begin{itemize}
  \tightlist
  \item
    describe maintenance of lists (Rebecca)
  \end{itemize}
\end{itemize}

The website provides an interface to the Google forms and spreadsheets
with template pages for viewing the list, adding a name to the list, and
finding additional resources. Importantly, our website creation tool is
hosted for free by GitHub, which provides a free website for each GitHub
organization (citation). Basic tools and skills required to set up a
Diversify site include knowledge of, or experience with, the version
control tool git, the webtool GitHub, and a text editor. A tutorial in
the DiversifyMicrobiology repository on GitHub provides links to these
resources and instructions for adapting the tool to your own field.

@@

A.K.H. collected the data, assigned demographics, analyzed the data, and
created the website. R.M.P. created the Google lists, forms, and website
content and the description of their maintenance. J.L. wrote the
introduction and provided conceptual advice. All authors contributed to
the final manuscript.

@@

\hypertarget{refs}{}

>>>>

Long-standing systemic bias, sexism, and racism have contributed to the
underrepresentation of many racial and ethnic groups, as well as women,
in science, technology, engineering, and math (STEM) fields (NIH 2015
report, Measuring DEI 2016, (1)). Organization climate and culture that
supports inclusion of all individuals is essential to support the
retention of historically underrepresented minorities (HURM) in the
U.S., as well as non-Caucasian individuals, and women in STEM fields
(Schneider, 2013). Inclusive organization culture will not suffice in
retaining HURM, non-Caucasian individuals, and women without
organization policy changes that support their values and goals (2).

A long-standing issue within STEM fields, specifically within academia,
has been a lack of diverse representation of scientists for trainees
(graduate students and postdoctoral fellows). In order to maintain
retention of HURM, non-Caucasian individuals, and women in STEM fields,
it is important for trainees to have visual representations of
themselves as scientists. The importance of representation in retaining
a diverse group of individuals in STEM fields is supported by social
role theory (3). Individuals tend to make inferences about
characteristics that are needed to be successful in a given role by
examining individuals that most occupy that role (3, 4). Therefore,
trainees who do not see representation of themselves in senior
scientific positions, or in this case as senior faculty members, may
decide that they do not possess the characteristics that are required to
succeed. In an attempt to make science a more inclusive environment,
many individuals have attempted to address this issue by promoting the
inclusion of more women speakers at conferences (5--7). However, no
study to date has addressed invited speaker seminar series diversity
within their own institution.

Within the Department of Microbiology and Immunology at the University
of Michigan (Ann Arbor, MI, USA), each year from September to June,
faculty members have the opportunity to invite scientists from other
institutions to give a one-hour seminar in which all department members
attend. The invited seminar speaker also has the opportunity to meet
with current department faculty members and trainees. Scientists who are
invited to give seminars are widely regarded as successful and the top
in their field. Thus, if trainees are constantly being exposed to ``the
top scientist in their field'', according to social role theory, it is
imperative that the selected seminar speakers represent a diverse group
of individuals.

In this study, we examine and compare the proportion of HURM,
non-Caucasian/non-HURM, and women invited speakers to white males in the
Department of Microbiology and Immunology. Additionally, we compare
invited-speaker demographics to the current trainee demographics as a
means to gauge if trainee demographics are being represented accordingly
throughout the seminar series. Following our investigation, we proposed
a policy change to the Department of Microbiology and Immunology in how
invited speakers are selected as a means to promote inclusion in our
department and reduce stereotype threat, microaggressions, and
unconscious bias. In order to facilitate inviting a more diverse group
of scientists, we developed a set of resources that allow scientists,
within the field of microbiology, to self-identify as an HURM,
non-Caucasian/non-HURM, or a woman. These resources will promote
inclusion and diversity by providing greater representation of all
scientists and will provide hosts an opportunity to invite a more
diverse group of scientists.

@@

Data were analyzed and figures generated in R Statisical Software, using
the tidyverse package ({\textbf{???}}).

@@

To understand the representation of women, we compared the proportion of
women in each academic role. At the trainee level, more than half of
students and postdoctoral fellows were women. That dropped to 46.77\% of
faculty hosts and 38.73\% of the invited speakers (Fig. 1A). Of 27
lectureships over the five year period, 37.04\% were awarded to women.
The proportion of women as faculty hosts and speakers is equivalent to
global estimates that 40\% of microbiologists are women, with a slightly
lower representation of women in lectureships (8).

@@

\begin{itemize}
\item
  HURM represent 10\% of assistant prof, falls to 5\% of full (9)
\item
  2017 doctorates in Micro/immuno = 26,250 -- ({\textbf{???}}) HURM =
  10.67 -- 11\% NCNH = 22.1 -- 22\%
\end{itemize}

@@

Several papers have investigated the representation of women at
scientific conferences, however, we have only identified one that
focused on invited speakers at universities (10). In their study,
\textbf{???}, examined 3,652 talks at 50 U.S. institutions in 2013 -
2014 and found that women faculty are less likely to be invited
speakers, despite similar acceptance rates. These results suggest that
women faculty are less often invited as speakers, a decision that may be
negatively impacted by assumptions about competency and dedication. The
dedication of women who have children to their work is perceived to be
less than that of their colleagues, i.e., men who also have children.
The perceived prioritization and commitments of women to family over
work may cause faculty to doubt their acceptance of a speaking
invitation (despite the prestigious nature of these invitations and
evidence to the contrary)({\textbf{???}}, 10). As a result, the faculty
member invites a different colleague who they feel is more likely to
agree (and is a man). Departments have different processes and criteria
for selecting invited speakers, but it is a matter of pride to bring the
best scientists possible. It may be that the definition of ``best''
poses a problem to women, who need three-times as many publications as
their men colleges to be considered equally competent. Some departments
only invite tenured faculty, which severely limits the number of
potential women speakers. Another scenario is that pre-tenure faculty
members invite prestigious, tenured faculty in their field to network
and secure letters for their own tenure package. The increased burden of
women to prove competency decreases their likelihood to be considered
for either tenure or as possible source of tenure letters.

The desire to invite the ``best'' scientist to these seminar series also
poses a problem for HURM and NCNH scientists. Both men and women who
identify as HURM and Asian reported having to work harder than their
white male colleagues to be perceived as legitimate scholars (11). The
proportion of HURM faculty at the Assistant and Associate Professor
level is currently higher than the Full Professor level so it will be
difficult to increase speaker diversity if early-career researchers are
not being considered (9). These differences in performance expectations
and patterns of exclusions are consistent themes in studies
characterizing the HURM faculty experience (12, 13). These experiences
decrease the opportunities for HURM and NCNH scientists to network,
secure letters for their own tenure package, and promote their work for
consideration of award nominations.

@@

\section{Instituting policy change within the Department of Microbiology
and
Immunology}\label{instituting-policy-change-within-the-department-of-microbiology-and-immunology}

In an attempt to promote inclusion within the Dept. M\&I these data were
presented to faculty members and the dept chair (Harry Mobley). Since,
trainee demographics were not represented within seminar speaker
demographics over the past 5 years, we proposed a policy change as to
how seminar speakers were being invited. This policy change included
switching from PI invited to lab invited in an attempt to allow trainees
to choose a speaker that best represented themselves. In addition to
this we also created resources which allowed scientists to self-identify
and provide host faculty with more diverse choices.

@@

The self-nomination form is a Google Form with entries logged in a
private Google Sheet. This form is embedded within the website and can
be linked to directly. The use of a Google Forms allows us to maintain
this database at no cost and gives us the flexibility to add questions
or change response options without disrupting previous responses.
Entries are logged in a private spreadsheet so that entries can be
screened before being added to the public database. This screening
currently includes two steps: 1. Confirming that each person is listed
in the database only once. 2. Verifying that the submitted website is a
professional website for the person being listed. If a person has not
been listed in the database previously and passes step 2, a new entry is
added to the public database spreadsheet. If a person is already listed
in the database, their information is updated to the most recent
submission.

This public spreadsheet is embedded in the website and can be open
separately as a locked (uneditable) Google Sheet. Importantly, this
allows the list to be easily searched. We have chosen to list
individuals' academic information first in the spreadsheet to encourage
a focus on academic achievement rather than tokenization of marginalized
identities. Currently the database lists individuals in order of
self-nomination but future versions will be re-sorted based on name
and/or academic field to varying the individuals who may receive more
attention for simply being at the top of the list.

The website provides an interface to the Google forms and spreadsheets
with template pages for viewing the list, adding a name to the list, and
finding additional resources. Importantly, our website creation tool is
hosted for free by GitHub, which provides a free website for each GitHub
organization. Basic tools and skills required to set up a Diversify site
include knowledge of, or experience with, the version control tool git,
the webtool GitHub, and a text editor. A tutorial in the
DiversifyMicrobiology repository on GitHub provides links to these
resources and instructions for adapting the tool to your own field.

@@

A.K.H. collected the data, assigned demographics, analyzed the data, and
created the website. R.M.P. created the Google lists, forms, and website
content and the description of their maintenance. J.L. wrote the
introduction and provided conceptual advice. All authors contributed to
preparing the final manuscript.

@@

\hypertarget{refs}{}
\hypertarget{ref-colloquy_2012}{}
1. 2012. Colloquy on minority males in science, technology, engineering,
and mathematics. National Academies Press.

\hypertarget{ref-Coe2019}{}
2. \textbf{Coe IR}, \textbf{Wiley R}, \textbf{Bekker L-G}. 2019.
Organisational best practices towards gender equality in science and
medicine. The Lancet \textbf{393}:587--593.
doi:\href{https://doi.org/10.1016/s0140-6736(18)33188-x}{10.1016/s0140-6736(18)33188-x}.

\hypertarget{ref-Eagly1984}{}
3. \textbf{Eagly AH}, \textbf{Steffen VJ}. 1984. Gender stereotypes stem
from the distribution of women and men into social roles. Journal of
Personality and Social Psychology \textbf{46}:735--754.
doi:\href{https://doi.org/10.1037/0022-3514.46.4.735}{10.1037/0022-3514.46.4.735}.

\hypertarget{ref-Carter2018}{}
4. \textbf{Carter AJ}, \textbf{Croft A}, \textbf{Lukas D},
\textbf{Sandstrom GM}. 2018. Women's visibility in academic seminars:
Women ask fewer questions than men. PLOS ONE \textbf{13}:e0202743.
doi:\href{https://doi.org/10.1371/journal.pone.0202743}{10.1371/journal.pone.0202743}.

\hypertarget{ref-kalejta_gender_2017}{}
5. \textbf{Kalejta RF}, \textbf{Palmenberg AC}. 2017. Gender Parity
Trends for Invited Speakers at Four Prominent Virology Conference
Series. Journal of Virology \textbf{91}.
doi:\href{https://doi.org/10.1128/JVI.00739-17}{10.1128/JVI.00739-17}.

\hypertarget{ref-casadevall_presence_2014}{}
6. \textbf{Casadevall A}, \textbf{Handelsman J}. 2014. The Presence of
Female Conveners Correlates with a Higher Proportion of Female Speakers
at Scientific Symposia. mBio \textbf{5}.
doi:\href{https://doi.org/10.1128/mBio.00846-13}{10.1128/mBio.00846-13}.

\hypertarget{ref-klein_speaking_2017}{}
7. \textbf{Klein RS}, \textbf{Voskuhl R}, \textbf{Segal BM},
\textbf{Dittel BN}, \textbf{Lane TE}, \textbf{Bethea JR}, \textbf{Carson
MJ}, \textbf{Colton C}, \textbf{Rosi S}, \textbf{Anderson A},
\textbf{Piccio L}, \textbf{Goverman JM}, \textbf{Benveniste EN},
\textbf{Brown MA}, \textbf{Tiwari-Woodruff SK}, \textbf{Harris TH},
\textbf{Cross AH}. 2017. Speaking out about gender imbalance in invited
speakers improves diversity. Nature Immunology \textbf{18}:475--478.
doi:\href{https://doi.org/10.1038/ni.3707}{10.1038/ni.3707}.

\hypertarget{ref-allagnat_gender_2017}{}
8. \textbf{Allagnat L}, \textbf{Berghmans S}, \textbf{Falk-Krzesinski
HJ}, \textbf{Hanafi S}, \textbf{Herbert R}, \textbf{Huggett S},
\textbf{Tobin S}. 2017. Gender in the global research landscape.

\hypertarget{ref-whittaker_retention_2015}{}
9. \textbf{Whittaker JA}, \textbf{Montgomery BL}, \textbf{Martinez
Acosta VG}. 2015. Retention of Underrepresented Minority Faculty:
Strategic Initiatives for Institutional Value Proposition Based on
Perspectives from a Range of Academic Institutions. Journal of
undergraduate neuroscience education: JUNE: a publication of FUN,
Faculty for Undergraduate Neuroscience \textbf{13}:A136--145.

\hypertarget{ref-nittrouer_gender_2018}{}
10. \textbf{Nittrouer CL}, \textbf{Hebl MR}, \textbf{Ashburn-Nardo L},
\textbf{Trump-Steele RCE}, \textbf{Lane DM}, \textbf{Valian V}. 2018.
Gender disparities in colloquium speakers at top universities.
Proceedings of the National Academy of Sciences \textbf{115}:104--108.
doi:\href{https://doi.org/10.1073/pnas.1708414115}{10.1073/pnas.1708414115}.

\hypertarget{ref-noauthor_seeking_2013}{}
11. 2013. Seeking Solutions: Maximizing American Talent by Advancing
Women of Color in Academia: Summary of a Conference. National Academies
Press, Washington, D.C.

\hypertarget{ref-pololi_race_2010}{}
12. \textbf{Pololi L}, \textbf{Cooper LA}, \textbf{Carr P}. 2010. Race,
Disadvantage and Faculty Experiences in Academic Medicine. Journal of
General Internal Medicine \textbf{25}:1363--1369.
doi:\href{https://doi.org/10.1007/s11606-010-1478-7}{10.1007/s11606-010-1478-7}.

\hypertarget{ref-hassouneh_experiences_2014}{}
13. \textbf{Hassouneh D}, \textbf{Lutz KF}, \textbf{Beckett AK},
\textbf{Junkins EP}, \textbf{Horton LL}. 2014. The experiences of
underrepresented minority faculty in schools of medicine. Medical
Education Online \textbf{19}:24768.
doi:\href{https://doi.org/10.3402/meo.v19.24768}{10.3402/meo.v19.24768}.
